Using an SMT engine to generate Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-21 2017-Xudong-SMT/ActaInformatica.tex
small TODO editins

\begin{proof}
  \TODO{I tentatively copied the proof here, from RR-8898.
the proof of the finiteness theorem refers to SOS rules Tr1 and
  Tr2. So maybe we must include (and explain) these here. One problem
  is that these rules have been modified/improved with each new
  publication of pNets papers, so we have to decide which version we
  use here
    Then we should
    check if it is sufficient with this version of the algorithm, or
    if it can be make more precise (some added analysis of the
    behavior of matching/combining/filetring ?)}
  The possible set of states of the open-automaton is the cartesian
  product of the states of its leaves $pLTS_i^{i\in L}$, that is finite by
  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
  number of applications of rules Tr2 on the structure of the
  pNet tree, with a finite number of synchronisation vectors applying
  at each node the number of global open transition is finite. Similarily rule Tr1 is 
  applied finitely if the number
  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
  \end{proof}

@@

\TODO{Candidate theorems: Xudong: state the theorems, and sketch the proofs}

\ERIC{First the good case: if we have no assignments to state variables in
the system, then we can directly compute the reachable part of the
automaton using the on-the-fly algorithm.}

\begin{theorem}[Correctness without assignments]
  \label{Th:finiteness}
If a pNet contains no assignment to state variables, then the smart
algorithm, without final reachability computation, computes exactly
the same open automaton as algorithm 1.
  \end{theorem}

@@

\ERIC{But in presence of assignments, we need to collect all of them
  before using the assignment information to refine the SAT
  checking. Still, the smart strategy will explore a reduced state
  space, but not the minimal one (discussion later)}

\begin{theorem}[Correctness without assignments]
  \label{Th:finiteness}
In the general case, then the smart
algorithm, with a final reachability computation, computes exactly
the same open automaton as algorithm 1.
\end{theorem}

@@

The safety
property \emph{``There is always a possibility to reset the system
  after a single failure''} (\ie without
  additional failures having to occur in the meantime) enforced by the
  Failure Monitor architecture can be specified using CTL as
    $\AG
\bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
  \PortReset}\bigr)$.  Additional properties are provided in \ref{TimerRR}.

>>>>

\begin{proof}
  \TODO{I tentatively copied the proof here, from RR-8898.
the proof of the finiteness theorem refers to SOS rules Tr1 and
  Tr2. Yuxin, I agree this proof is NOT required in this paper. But for the
  sake of reviewing process, (and if I find enough time), I will try
  to add an appendix with the semantic rules (constructing open
  transitions from pNets) and the proof of finiteness below }

  The possible set of states of the open-automaton is the cartesian
  product of the states of its leaves $pLTS_i^{i\in L}$, that is finite by
  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
  number of applications of rules Tr2 on the structure of the
  pNet tree, with a finite number of synchronisation vectors applying
  at each node the number of global open transitions is finite. Similarily rule Tr1 is 
  applied finitely if the number
  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
  \end{proof}

@@

The easy case is when the system does not contain assignments to state
variables. This does not mean ``data-independancy'': we can still have
guards in the pLTS transitions and in the synchronisation vectors,
making the behaviour depending on the value of input variables. But
the open automaton need not collect the set of possible values deal
with the values of local variables, so we can directly compute the
reachable part of the automaton using the on-the-fly algorithm.

\begin{theorem}[Correctness without assignments]
  \label{Th:CorrectnessWithoutAssignments}
If a pNet contains no assignment to state variables, then the smart
algorithm, without final reachability computation, computes exactly
the same open automaton as algorithm 1.
  \end{theorem}

@@

But in presence of assignments, we need to collect all of them
  before using the assignment information to refine the SAT
  checking. Still, the smart strategy will explore a reduced state
  space, but not the minimal one (discussion later).

\begin{theorem}[Correctness without assignments]
  \label{Th:CorrectnessWithAssignments}
In the general case, then the smart
algorithm, with a final reachability computation, computes exactly
the same open automaton as algorithm 1.
\end{theorem}

@@

The safety
property \emph{``There is always a possibility to reset the system
  after a single failure''} (\ie without
  additional failures having to occur in the meantime) enforced by the
  Failure Monitor architecture can be specified using CTL as
    $\AG
\bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
  \PortReset}\bigr)$.  Additional properties are provided in \cite{TimerRR}.
